---
title: "Final Report"
date: "05-30-2024"
author:
  - name: Ana Bendiek Laranjo
    orcid: 0009-0006-1720-6031
    email: abendiek@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
abstract: 
  The abstract will be placed here. Breaks can be added by hitting return on the keyboard.
license: "CC BY"
citation: 
  container-title: My Blog
  url: https://www.example.com
bibliography: references.bib
csl: apa.csl
format:
  html:
    embed-resources: true
    toc: true
    
pdf: default
execute:
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---

------------------------------------------------------------------------

# Introduction

The survey's main research question is:

How do professionals in the architecture, engineering, and construction
(AEC) industries in the DACH region adopt digital twins and circular
strategies, and what is the potential for digital twins to support
circular construction practices?

To answer the main research question, three initial research questions
are guiding the study:

-   **RQ1:** What is the current level of awareness ?

-   **RQ2:** To what extent are circular economy strategies currently
    being adopted and implemented by AEC professionals in the DACH
    region?

-   **RQ3:** How do AEC professionals in the DACH region envision the
    potential of digital twins to support and enhance circular
    construction practices?

Current research on this topic includes 

1.  defining “Digital Twins” on a general and industry-specific level
    [(Grieves, 2015; Thelen et al.,
    2022)](https://www.zotero.org/google-docs/?TZ848a)

2.  the identification of (potential) applications of Digital Twins in
    the construction sector [(Davila Delgado and Oyedele, 2021; Ammar et
    al., 2022; Araújo et al., 2022; AlBalkhy et al.,
    2024)](https://www.zotero.org/google-docs/?XEJlyF)

3.  the potential applications of Digital Twins for circular strategies
    in construction [(Meng, Das and Meng,
    2023)](https://www.zotero.org/google-docs/?H2cgcw) and other
    industries [(Preut, Kopka and Clausen, 2021; Mügge et al.,
    2024)](https://www.zotero.org/google-docs/?8TzmjP)

These research studies denote significant progress in understanding the
applications of digital twins (DT) in the AEC industries. Nevertheless,
a significant knowledge gap remains regarding the real-world DT adoption
levels in the AEC industry. DT adoption encompasses the awareness,
understanding, and acceptance among industry stakeholders.

Evaluating awareness levels involves determining how individuals and
organizations within the BE sector know the DT concept and its potential
benefits. Understanding levels refer to the depth of comprehension
regarding the intricacies and implications of DT implementation. This
research aspect also covers identifying the skills required to build DT
systems. Acceptance involves examining the willingness of stakeholders
to adopt DT technologies and integrate them into their operational
frameworks.

This research is exploratory and aims to set a precedent for future
industry adoption.

# Methods

## Data collection

The study is designed as an online survey, with data being collected
through a survey platform. This approach allows the researchers to gain
insights into the state of the industry in different geographic
locations, particularly in relation to the adoption of new technologies.

The study will be conducted transparently, with no incomplete disclosure
of information or deception involved. Participants will be provided with
a link to the survey, which they can access via email or LinkedIn. They
can choose to complete the survey from any location they prefer.

Participants will be free to stop the survey at any time, ensuring their
autonomy and voluntary participation. Data collection will be
facilitated through the use of Google Forms or Qualtrics, two widely
used survey platforms.

## Participants

The study is limited to people in the Architecture, Engineering, and
Construction (AEC) industry in Germany, Austria, and Switzerland. The
researchers expect a minimum of 30 participants (10 participants per
country) for the study, which would still provide valuable insights to
report on. At the same time, a reasonable upper limit for the number of
participants is set at around 10% of the population size or a maximum of
1000 per included country (Austria, Germany, Switzerland), as the survey
will be distributed to a few professional working groups focused on
similar topics.

The general inclusion criteria for the study will be based on the
participants' actual work experience in the architecture, engineering,
and construction industries. Initial questions will also assess their
knowledge and experience in areas such as digital twins and the circular
economy.

While the questions about the targeted, relevant experience will not
necessarily be used to exclude participants, they will help qualify the
potential responses and provide more context for the researchers to
interpret the data. Furthermore, information regarding the sex and
gender of the participants will be requested to conduct sex—and
gender-based analyses (SGBA).

# Results

```{r}
library(ggplot2)
```

## Figures
### Awareness of ETH Sustainability Department and Net Zero Initiative

```{r}
ggplot(awareness_summary, aes(x = Initiative, y = Percentage, fill = Initiative)) +
  geom_bar(stat = "identity") +
  labs(title = "Awareness of ETH Sustainability Department and Net Zero Initiative",
       x = "Initiative",
       y = "Percentage") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Awareness of Net Zero measures

```{r}
ggplot(net_zero_measures, aes(x = reorder(Measure, -Percentage), y = Percentage)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Awareness of Net Zero Measures",
       x = "Percentage",
       y = "Measure",
       fill = "Awareness") +
  coord_flip() +
  theme_minimal()
```

### What is the most effective information channel?

```{r}
ggplot(learning_channel_count, aes(x = fct_reorder(learn_net_zero, n), y = n)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Most Important Information Channel for Learning about ETH Net Zero",
       x = "Learning Channel",
       y = "Frequency") +
  coord_flip() 

```

### What is the most promising information channel to increase the visibility?

```{r}

```


## Tables


# Conclusions

# References

In @tilley2021my, the authors describe how visitors still expect a
personal pick-up, despite the availability of taxi services
