---
title: "ETH Sustainability Department Visibility Survey"
subtitle: "Final report of the Capstone Project "
date: "05-30-2024"
author:
  - name: Ana Bendiek Laranjo
    orcid: 0009-0006-1720-6031
    email: abendiek@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
abstract: "This survey aims to assess the visibility and awareness of the ETH Sustainability department among ETH Zurich members. As the central hub for sustainability activities, ETH Sustainability is crucial in advancing sustainable development within the university and in broader society.

The department oversees various initiatives, including ETH Net Zero activities, sustainability reporting, and various projects related to sustainable travel and gastronomy. Despite its pivotal role, there is limited information on the awareness levels and engagement of the ETH community with these initiatives.

The survey seeks to understand the current recognition and understanding of ETH Sustainability’s work and services. Specifically, it will explore how well the department's efforts are known among students, faculty, and staff, and how these stakeholders perceive and engage with its activities. Additionally, the survey will gather insights on potential strategies to enhance the department's visibility and improve stakeholder engagement. The findings will contribute to the ongoing efforts to integrate sustainability more deeply into the university’s culture and operations, ensuring that ETH Zurich continues to lead in sustainable development."
license: "CC BY"
bibliography: references.bib
csl: apa.csl
format:
  html:
    embed-resources: true
    toc: true
    code-fold: true
pdf: default
execute:
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---

------------------------------------------------------------------------

# Introduction

Switzerland derives its concept of sustainability from the World
Commission on Environment and Development [@are2024nachhaltigkeit], also
known as the Brundtland Commission. In its 1987 report, "Our Common
Future," the Commission defined sustainable development as "Development
that satisfies the needs of the present without jeopardizing the ability
of future generations to meet their own needs" [@wced1991our]. Based on
the 2030 Agenda of 2015 [@un2015transforming¨], the Federal Council
adopted Switzerland's long-term climate strategy on 27 January 2021. In
the "Strategie Nachhaltige Entwicklung 2030", the Confederation
undertakes to consistently apply the principles of sustainable
development to its own activities and units, which include the ETH
Domain, in order to contribute to the achievement of the SDS 2030 goals
[@are2021strategie].

Within the organizational structure of ETH Zurich, the Department of
Sustainability is the central strategic-operational unit and dedicated
to enhancing ETH Zurich's contribution to sustainable development and
communicating these efforts both internally and externally. The unit was
established in 2008 and has since initiated numerous groundbreaking
projects and processes. Their responsibilty lies in the coordination of
the ETH Net Zero activities, manage sustainability reporting, oversee
the ETH Air Travel Project and the Sustainable Gastronomy Project,
compile the catalogue of sustainability-related lectures, and organize
the Public Lecture series "Sustainable Development Goals in Context" in
collaboration with ETH4D [@ethsusdep2024]. Despite its crucial role in
the compliance with climate change targets, there is limited information
on the awareness levels and engagement of the ETH community with these
initiatives.

The survey seeks to understand the current awareness and understanding
of ETH Sustainability’s work and services. Specifically, it will explore
how well the department's efforts are known among members of the ETH
domain, and how these stakeholders perceive and engage with its
activities. The insights of this study could contribute to improving the
department's visibility and increasing sustainability on campus.

The survey's main research question is: What is the current level of
awareness among ETH members regarding the work of and services provided
by the ETH Sustainability department, and how could it be improved?

To answer the main research question, three initial research questions
are guiding the study:

-   **RQ1:** What is the current level of awareness among ETH members
    about the ETH Sustainability Department and its work?
-   **RQ2:** How visible is the work of the ETH Sustainability
    Department?
-   **RQ3:** What would most effective information channels to increase
    the visibility of the ETH?

This project is part of the lecture series "151-8102-00L Research Beyond
the Lab: Open Science and Research Methods for a Global Engineer" by
Prod. Elizabeth Tilley and Lars Schöbitz. The research is exploratory
and aims to set a precedent for future information diffusion.

# Methods

The study was designed as an online survey, with data being collected
through the Google Forms platform. The study was conducted
transparently, with no incomplete disclosure of information or deception
involved. Participants were provided with a link to the survey, which
they could access via email. They could choose to complete the survey
from any location they prefer. Furthermore, participants were free to
stop the survey at any time, ensuring their autonomy and voluntary
participation.

The study was limited to people from the ETH domain, including the
research institutions Paul Scherrer Institute (PSI), the Swiss Federal
Institute for Forest, Snow and Landscape Research (WSL), the Swiss
Federal Laboratories for Materials Science and Technology (Empa), and
the Swiss Federal Institute of Aquatic Science and Technology (Eawag).
To gain insights on the awareness levels among different affilition
groups and locations, the participants were asked to provide information
on their group and primarily working location.

Responses were timestamped and collected over a one-week period,
ensuring a comprehensive snapshot of the university community's current
awareness and engagement levels. The survey was first published on May
24, 2024 and was closed on May 31, 2024 with a total of 24 participants.

The collected data were then analyzed to identify trends, gaps, and
potential strategies for enhancing the visibility and impact of the ETH
Sustainability department.

# Results

In this sections the survey data is analysed to answer the initial
research questions.

```{r setup, include=FALSE}
#Load packages
library(dplyr)
library(DT)
library(ggplot2)
library(ggthemes)
library(googlesheets4)
library(gt)
library(gtsummary)
library(knitr)
library(readr)
library(scales)
library(stringr)
library(tidyverse)

#Read file
eth_dep_sus_visibility_visual <- read_csv("/cloud/project/data/processed/eth_dep_sus_visibility_processed.csv")

```

### **What is the current level of awareness among ETH members about the ETH Sustainability Department and its work?**

Among the participants 14 out of 21 participants had heard of it
previous to the study. Unabhängig von dieser Antwort, wurde in der
Studie zudem untersucht, inwieweit die ETH member die inititiven des ETH
departements kennen. Die Ergebnisse sind in @fig-initiatives
dargestellt.

```{r}
#| label: fig-initiatives
#| fig-cap: Awareness of the ETH Sustainability Department and its initiatives among ETH domain members.
#| fig-align: left

# data analysis --------------------------------------
initiative_names <- c(
  heard_eth_sus = "ETH Sustainability Department",
  heard_net_zero = "ETH Net Zero",
  heard_net_zero_day = "ETH Net Zero Day",
  heard_air_travel = "Air Travel Project",
  heard_sus_gastronomy = "Sustainable Gastronomy Project",
  heard_sdg_lecture = "SDG Public Lectures"
)

awareness_dep_sus_ini <- eth_dep_sus_visibility_visual %>%
  select(heard_eth_sus, heard_net_zero, heard_net_zero_day, heard_air_travel, heard_sus_gastronomy, heard_sdg_lecture) %>%
  pivot_longer(cols = everything(), names_to = "Initiative", values_to = "Response") %>%
  mutate(Initiative = recode(Initiative, !!!initiative_names)) %>%
  mutate(Initiative = factor(Initiative, levels = initiative_names)) %>%
  group_by(Initiative, Response) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Response = factor(Response, levels = c("No", "Yes", "N/A")))

# results display as visualisation --------------------------------------
ggplot(data = awareness_dep_sus_ini, aes(x = Initiative, y = Count, fill = Response)) +
  geom_bar(stat = "identity") +  # Keep the default stacking order
  geom_text(aes(label = Count), position = position_stack(vjust = 0.5), color = "white") +  # Change text color to white
  labs(title = "Awareness of ETH Sustainability Department and Net Zero Initiative",
       x = "Initiative",
       y = "Count",
       fill = "Response") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(color = "black", angle = 0, hjust = 0.5, vjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 15))  # Increase margin at the top of the x-axis title
  ) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_fill_colorblind()

# save data underlying the table ----------------------
write_csv(awareness_dep_sus_ini, "/cloud/project/data/final/awareness_department_initiatives.csv")

```

Um zu kontrastieren, ist in @fig-yesinitiatives dargestellt, wie bekannt
die Initiativen unter den Leuten sind, die angegeben haben, die Arbeit
des Departements zu kennen.

```{r}
#| label: fig-yesinitiatives
#| fig-cap: Awareness of the ETH Sustainability Department and its initiatives among ETH domain members who responded Yes to hearing about the Sustainability Department.
#| fig-align: left

# Filter data for participants who responded "Yes" to hearing about the Sustainability Department
awareness_dep_sus_ini_filtered <- eth_dep_sus_visibility_visual %>%
  filter(heard_eth_sus == "Yes") %>%
  select(heard_eth_sus, heard_net_zero, heard_net_zero_day, heard_air_travel, heard_sus_gastronomy, heard_sdg_lecture) %>%
  pivot_longer(cols = everything(), names_to = "Initiative", values_to = "Response") %>%
  mutate(Initiative = recode(Initiative, !!!initiative_names)) %>%
  mutate(Initiative = factor(Initiative, levels = initiative_names)) %>%
  group_by(Initiative, Response) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Response = factor(Response, levels = c("No", "Yes", "N/A")))

# results display as visualisation --------------------------------------
ggplot(data = awareness_dep_sus_ini_filtered, aes(x = Initiative, y = Count, fill = Response)) +
  geom_bar(stat = "identity") +  # Keep the default stacking order
  geom_text(aes(label = Count), position = position_stack(vjust = 0.5), color = "white") +  # Change text color to white
  labs(title = "Awareness of ETH Sustainability Department and Net Zero Initiative (Among Participants who Heard about the Sustainability Department)",
       x = "Initiative",
       y = "Count",
       fill = "Response") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(color = "black", angle = 0, hjust = 0.5, vjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 15))  # Increase margin at the top of the x-axis title
  ) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_fill_colorblind()

# save data underlying the table ----------------------
write_csv(awareness_dep_sus_ini_filtered, "/cloud/project/data/final/awareness_department_initiatives_filtered.csv")
```

Aus beiden figrues (@fig-initiatives, @fig-yesinitiatives) geht hervor,
dass the "Net Zero initiative" is the most known (66% of participants
heard of it), followed by the SDG Public Lecture Series and the
Sustainable Gastronomy Project (33% of participants heard of it
respectively).

To explore how aware ETH members were of this initiative further
questions were asked regarding specific ETH Net Zero measures.
Specifically, participants were first asked to assess their familiarity
with the Net Zero on a scale from "not familiar at all" to "very
familiar" and then which of these measures they heard of. From
@fig-netzeromeasures it is visible, that the "Decarbonized Campus"
initiative is the most known.

```{r}
#| label: fig-netzeromeasures
#| fig-cap: Awareness of Net Zero initiative among ETH domain members.
#| fig-align: left

## What is the awareness of the Net Zero measures among the people that have heard of the Net Zero initiative?
# data analysis --------------------------------------
measure_labels <- c(
  heard_measure_dec_campus = "Decarbonised campus",
  heard_measure_indirect_emissions = "Reduction of indirect emissions from electricity procurement and district heating",
  heard_measure_living_lab = "Campus as a net-zero living lab",
  heard_measure_bus_travel = "Emission-reduced business travel",
  heard_measure_scope3 = "Scope 3 exploration",
  heard_measure_procurement = "Emission-reduced procurement of goods, construction and services",
  heard_measure_community_engage = "Communication and Community Engagement",
  heard_measure_data_monitor = "Data Availability, Monitoring and Reporting",
  heard_measure_expertise = "Strengthening Expertise in Sustainability and Ethics"
)

awareness_net_zero_measures <- eth_dep_sus_visibility_visual %>%
  select(starts_with("heard_measure_")) %>%
  summarise_all(~sum(. == "Yes", na.rm = TRUE) / n()) %>%
  gather(key = "Measure", value = "Percentage") %>%
  mutate(Measure = recode(Measure, !!!measure_labels))

awareness_net_zero_measures <- awareness_net_zero_measures %>%
  mutate(Measure = str_wrap(Measure, width = 30))

# results display as visualisation --------------------------------------
ggplot(awareness_net_zero_measures, aes(x = reorder(Measure, -Percentage), y = Percentage)) +
  geom_bar(stat = "identity", fill = "#2a9d8f", width = 0.8) +  # Adjust bar width and color
  geom_text(aes(
    label = scales::percent(Percentage, accuracy = 1)), 
    hjust = -0.1, size = 3, color = "black") +  # Add percentage labels
  labs(title = "Awareness of Net Zero Measures",
       x = "Net Zero Measure",
       y = "Percentage of Respondents Aware") +
  coord_flip() +
  scale_y_continuous(labels = percent_format()) + 
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10, hjust = 1),
    panel.grid.major = element_line(linewidth = 0.1, color = "gray80"),
    panel.grid.minor = element_blank(),
  )

# save data underlying the table ----------------------
write_csv(awareness_net_zero_measures, "/cloud/project/data/final/awareness_net_zero_measures.csv")
```

### How visible is the work of the ETH Sustainability Department?

In this section, the responses regarding the visibility of the
department were analyzed. While the participant group expressed "very
high interest" in sustainability and climate change mitigation and
strong support for an ETH-wide sustainability strategy, the visibility
was rated at 2.40 on a scale from 0 (not visible at all) to 5 (very
visible). The statistical analysis of the results is presented in
@tbl-interests.

```{r}
#| label: tbl-interests
#| tbl-cap: "Summary of participants attitude towards sustainability, an ETH wide sustainability strategy and the perceived visibility"

# data analysis --------------------------------------
# interest_sustainability_tbl <- eth_dep_sus_visibility_visual %>%
#   summarize(
#     count = n(),
#     mean = mean(interest_sustainability, na.rm = TRUE),
#     median = median(interest_sustainability, na.rm = TRUE),
#     sd = sd(interest_sustainability, na.rm = TRUE)
#   ) %>%
#   mutate(category = "Personal interest in sustainability and climate change mitigation")

importance_eth_strategy_tbl <- eth_dep_sus_visibility_visual %>%
  summarize(
    count = n(),
    mean = mean(importance_eth_strategy, na.rm = TRUE),
    median = median(importance_eth_strategy, na.rm = TRUE),
    sd = sd(importance_eth_strategy, na.rm = TRUE)
  ) %>%
  mutate(category = "Importance of ETH-wide Sustainability Strategy")

vis_eth_sus_tbl <- eth_dep_sus_visibility_visual %>%
  summarize(
    count = n(),
    mean = mean(vis_eth_sus_work, na.rm = TRUE),
    median = median(vis_eth_sus_work, na.rm = TRUE),
    sd = sd(vis_eth_sus_work, na.rm = TRUE)
  ) %>%
  mutate(category = "Visibility of the ETH Sustainability Department")

summary_table <- bind_rows(
  #interest_sustainability_tbl,
  importance_eth_strategy_tbl,
  vis_eth_sus_tbl
) %>%
  select(category, everything())

# results display as visualisation --------------------------------------
summary_table %>%
  gt() %>%
  tab_header(
    title = "Summary of Participant's Beliefs",
    subtitle = "Importance, and Visibility"
  ) %>%
  cols_label(
    category = "Category",
    count = "Count",
    mean = "Mean",
    median = "Median",
    sd = "Standard Deviation"
  ) %>%
  fmt_missing(
    columns = everything(),
    missing_text = "N/A"
  )

# save data underlying the table ----------------------
#write_csv(interest_sustainability_tbl, "/cloud/project/data/final/interest_sustainability_summary.csv")
write_csv(importance_eth_strategy_tbl, "/cloud/project/data/final/importance_eth_strategy_summary.csv")
write_csv(vis_eth_sus_tbl, "/cloud/project/data/final/visibility_eth_sustainability_summary.csv")
```

### What are the most effective information channels to increase the visibility of the ETH ETH Sustainability Department?

Participants were asked about the information channels through which
they would most likely learn about the department's work. According to
@fig-generalchannel, the ETH mailinglist and advertisement on campus are
the most promising.

```{r}
#| label: fig-generalchannel
#| fig-cap: Information diffusion channel considered most promising among ETH domain members.
#| fig-align: left

# Data analysis --------------------------------------
# Data preparation
visibility_data <- eth_dep_sus_visibility_visual %>%
  select(starts_with("notice_"))

# Count the number of TRUE values for each channel
visibility_counts <- visibility_data %>%
  summarise_all(~sum(. == TRUE, na.rm = TRUE))

# Reshape the data for plotting
visibility_counts_long <- visibility_counts %>%
  pivot_longer(cols = everything(), names_to = "Channel", values_to = "Count")

# Label mapping for the channels
channel_labels <- c(
  notice_ETH_main_website = "ETH website",
  notice_ETH_mailing_list = "ETH mailing list",
  notice_Advertisement_on_Campus = "Advertisement on campus",
  notice_ETH_Link_TV = "Advertisement on ETH-Link TV",
  notice_Lectures_and_seminars = "Lecture or seminar",
  notice_Social_Media = "Social Media (e.g. ETH Instagram account)"
)

# Apply the channel labels
visibility_counts_long <- visibility_counts_long %>%
  mutate(Channel = recode(Channel, !!!channel_labels))

# Visualization: Bar plot
ggplot(visibility_counts_long, aes(y = reorder(Channel, Count), x = Count, fill = Channel)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Count), hjust = 1.1, color = "black", size = 3) +  # Add count labels
  labs(title = "Visibility of Channels",
       x = "Count",
       y = "Channel") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10, hjust = 1),
    legend.position = "none"  # Remove the legend
  ) +
  scale_fill_manual(values = c(
    "ETH website" = "#A6CEE3",
    "ETH intranet" = "#1F78B4",
    "Advertisement on campus" = "#B2DF8A",
    "Advertisement on ETH-Link TV" = "#33A02C",
    "Lecture or seminar" = "#FB9A99",
    "Social Media (e.g. ETH Instagram account)" = "#E31A1C"
  ))

# Save data underlying the table
write_csv(visibility_counts_long, "/cloud/project/data/final/visibility_counts.csv")
```

This is contrasted by the most mentioned information source for the ETH
Net Zero initiative is "other students/colleagues." According to
@fig-netzerochannel most participants heard of the ETH Net Zero
initiative through other students and colleagues.

```{r}
#| label: fig-netzerochannel
#| fig-cap: Information diffusion channel of Net Zero Initiative among ETH domain members.
#| fig-align: left

## What information channel was the most effective?
# data analysis --------------------------------------
net_zero_learning <- eth_dep_sus_visibility_visual %>%
  filter(!is.na(learn_net_zero)) %>%
  filter(heard_net_zero == "Yes")

net_zero_info_channel_count <- net_zero_learning %>%
  count(learn_net_zero) %>%
  arrange(desc(n))

# results display as visualisation --------------------------------------
ggplot(net_zero_info_channel_count, aes(x = fct_reorder(learn_net_zero, n), y = n)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Most Important Information Channel for Learning about ETH Net Zero",
       x = "Information Channel",
       y = "Count") +
  coord_flip()

# save data underlying the table ----------------------
write_csv(net_zero_info_channel_count, "/cloud/project/data/final/net_zero_info_channel.csv")
```

# Conclusions

In summary, the following conclusions can be drawn:

-   The awareness of the ETH Department for Sustainability among
    participants is moderate, indicating potential opportunities for
    enhancing outreach efforts.

-   The Net Zero Initiative was identified as the most well-known
    initiative within the ETH community. Participants heard of the
    initiative mainly through other students and colleagues.

-   Despite the importance of sustainability, the department's
    visibility could be better, indicating a need for improved
    communication and promotional strategies.

-   Among the various information diffusion channels considered, the ETH
    mailing list and advertising the work on campus are the most
    effective for disseminating information about the department's
    activities and initiatives, highlighting its potential for
    increasing visibility and engagement.

However, it's important to acknowledge the study's limitations. Firstly,
the sample size may not be representative, with more participants from
the Hönggerberg campus than from other locations. Additionally, the
study's scope primarily encompasses the perspectives of a specific
demographic within the ETH community, potentially limiting its
generalizability. Future research could explore the department's
perceptions and awareness across diverse demographic groups and campuses
to provide a more comprehensive understanding of its visibility and
impact.

# References
