---
title: "ETH Sustainability Department Visibility Survey"
subtitle: "Final report of the Capstone Project "
date: "05-30-2024"
author:
  - name: Ana Bendiek Laranjo
    orcid: 0009-0006-1720-6031
    email: abendiek@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
abstract: "This survey aims to assess the visibility and awareness of the ETH Sustainability department among ETH Zurich members. As the central hub for sustainability activities, ETH Sustainability is crucial in advancing sustainable development within the university and in broader society.

The department oversees various initiatives, including ETH Net Zero activities, sustainability reporting, and various projects related to sustainable travel and gastronomy. Despite its pivotal role, there is limited information on the awareness levels and engagement of the ETH community with these initiatives.

The survey seeks to understand the current recognition and understanding of ETH Sustainability’s work and services. Specifically, it will explore how well the department's efforts are known among students, faculty, and staff, and how these stakeholders perceive and engage with its activities. Additionally, the survey will gather insights on potential strategies to enhance the department's visibility and improve stakeholder engagement. The findings will contribute to the ongoing efforts to integrate sustainability more deeply into the university’s culture and operations, ensuring that ETH Zurich continues to lead in sustainable development."
license: "CC BY"
citation: 
  container-title: My Blog
  url: https://www.example.com
bibliography: references.bib
csl: apa.csl
format:
  html:
    embed-resources: true
    toc: true
    code-fold: true
pdf: default
execute:
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---

------------------------------------------------------------------------

# Introduction

Switzerland derives its concept of sustainability from the World
Commission on Environment and Development [@are2024nachhaltigkeit], also known as the Brundtland
Commission. In its 1987 report, "Our Common Future," the
Commission defined sustainable development as "Development that
satisfies the needs of the present without jeopardizing the ability of
future generations to meet their own needs" [@wced1991our].
Based on the 2030 Agenda of 2015 [@un2015transforming¨], the Federal Council adopted Switzerland's long-term climate strategy on 27 January 2021. In the "Strategie Nachhaltige Entwicklung 2030", the Confederation undertakes to consistently apply the principles of sustainable development to its own activities and units, which include the ETH Domain, in order to contribute to the achievement of the SDS 2030 goals [@are2021strategie].

Within the organizational structure of ETH Zurich, the Department of
Sustainability is the central strategic-operational unit and dedicated
to enhancing ETH Zurich's contribution to sustainable development and
communicating these efforts both internally and externally. The unit was
established in 2008 and has since initiated numerous groundbreaking
projects and processes. Their responsibilty lies in the coordination of
the ETH Net Zero activities, manage sustainability reporting, oversee
the ETH Air Travel Project and the Sustainable Gastronomy Project,
compile the catalogue of sustainability-related lectures, and organize
the Public Lecture series "Sustainable Development Goals in Context" in
collaboration with ETH4D [@ethsusdep2024]. Despite its crucial role in the
compliance with climate change targets, there is limited information on
the awareness levels and engagement of the ETH community with these
initiatives.

The survey seeks to understand the current recognition and understanding
of ETH Sustainability’s work and services. Specifically, it will explore
how well the department's efforts are known among members of the ETH
domain, and how these stakeholders perceive and engage with its
activities. The insights of this study could contribute to improving the
department's visibility and increasing sustainability on campus.

The survey's main research question is: What is the current level of
awareness among ETH members regarding the work of and services provided
by the ETH Sustainability department, and how could it be improved?

To answer the main research question, three initial research questions
are guiding the study:

-   **RQ1:** What is the current level of awareness among ETH members
    about the ETH Sustainability Department?
-   **RQ2:** What is the current level of awareness among ETH members
    about the initiatives of the ETH Sustainability Department?
-   **RQ3:** What are the most effective information channels to
    increase the visibility of the ETH ETH Sustainability Department?

This research is exploratory and aims to set a precedent for future
information diffusion.

# Methods

The study was designed as an online survey, with data being collected
through the Google Forms platform.
The study was conducted transparently, with no incomplete disclosure of information or deception involved. Participants were provided with a link to the survey, which they could access via email. They could choose to complete the survey from any location they prefer. Furthermore, participants were free to stop the survey at any time, ensuring their autonomy and voluntary participation.

The study was limited to people from the ETH domain, including the
research institutions Paul Scherrer Institute (PSI), the Swiss Federal
Institute for Forest, Snow and Landscape Research (WSL), the Swiss
Federal Laboratories for Materials Science and Technology (Empa), and
the Swiss Federal Institute of Aquatic Science and Technology (Eawag).
To gain insights on the awareness levels among different affilition
groups and locations, the participants were asked to provide information
on their group and primarily working location.

Responses were timestamped and collected over a one-week period,
ensuring a comprehensive snapshot of the university community's current
awareness and engagement levels. The survey was first published on May
24, 2024 and was closed on May 31, 2024 with a total of 24 participants.

The collected data were then analyzed to identify trends, gaps, and
potential strategies for enhancing the visibility and impact of the ETH
Sustainability department.

# Results

```{r setup, include=FALSE}
library(dplyr)
library(DT)
library(ggplot2)
library(googlesheets4)
library(gt)
library(gtsummary)
library(knitr)
library(readr)
library(tidyverse)
```

## RQ1: What is the current level of awareness among ETH members about the ETH Sustainability Department?

The study shows, that overall the visibility of the ETH Department for Sustainability is low. Among the participants only


```{r}
eth_dep_sus_visibility_visual <- read_csv("/cloud/project/data/processed/eth_dep_sus_visibility_processed.csv")

# Calculate summary statistics for familiarity with ETH Sustainability Department's work
interest_sustainability_tbl <- eth_dep_sus_visibility_visual %>%
  summarize(
    count = n(),
    mean = mean(interest_sustainability, na.rm = TRUE),
    median = median(interest_sustainability, na.rm = TRUE),
    sd = sd(interest_sustainability, na.rm = TRUE)
  ) %>%
  mutate(category = "Familiarity with ETH Sustainability Department's Work")

importance_eth_strategy_tbl <- eth_dep_sus_visibility_visual %>%
  summarize(
    count = n(),
    mean = mean(importance_eth_strategy, na.rm = TRUE),
    median = median(importance_eth_strategy, na.rm = TRUE),
    sd = sd(importance_eth_strategy, na.rm = TRUE)
  ) %>%
  mutate(category = "Importance of ETH-wide Sustainability Strategy")

vis_eth_sus_tbl <- eth_dep_sus_visibility_visual %>%
  summarize(
    count = n(),
    mean = mean(vis_eth_sus_work, na.rm = TRUE),
    median = median(vis_eth_sus_work, na.rm = TRUE),
    sd = sd(vis_eth_sus_work, na.rm = TRUE)
  ) %>%
  mutate(category = "Visibility of the ETH Sustainability Department")

# Combine the summary tables into a single data frame
summary_table <- bind_rows(
  interest_sustainability_tbl,
  importance_eth_strategy_tbl,
  vis_eth_sus_tbl
) %>%
  select(category, everything())

# results display as visualisation --------------------------------------
#| label: tbl-summary-personal
#| tbl-cap: "Summary of participants attitude towards sustainability, an ETH wide sustainability strategy and the perceived visibility"
summary_table %>%
  gt() %>%
  tab_header(
    title = "Summary of Participant's Beliefs",
    subtitle = "Importance, and Visibility"
  ) %>%
  cols_label(
    category = "Category",
    count = "Count",
    mean = "Mean",
    median = "Median",
    sd = "Standard Deviation"
  ) %>%
  fmt_missing(
    columns = everything(),
    missing_text = "N/A"
  )

# save data underlying the table ----------------------
write_csv(interest_sustainability_tbl, "/cloud/project/data/final/interest_sustainability_summary.csv")
write_csv(importance_eth_strategy_tbl, "/cloud/project/data/final/importance_eth_strategy_summary.csv")
write_csv(vis_eth_sus_tbl, "/cloud/project/data/final/visibility_eth_sustainability_summary.csv")
```


## RQ2: What is the current level of awareness among ETH members about the initiatives of the ETH Sustainability Department?

Awareness of ETH Sustainability Department and its initiatives

```{r}
## Which initiative is the most known?

# data analysis --------------------------------------
initiative_names <- c(
  heard_eth_sus = "ETH Net Zero",
  heard_net_zero = "ETH Net Zero Day",
  heard_net_zero_day = "Air Travel Project",
  heard_air_travel = "Sustainable Gastronomy Project",
  heard_sus_gastronomy = "SDG Public Lectures"
)

awareness_dep_sus_ini <- eth_dep_sus_visibility_visual %>%
  select(heard_eth_sus, heard_net_zero, heard_net_zero_day, heard_air_travel, heard_sus_gastronomy, heard_sdg_lecture) %>%
  pivot_longer(cols = everything(), names_to = "Initiative", values_to = "Response") %>%
  group_by(Initiative, Response) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  mutate(Response = factor(Response, levels = c("Yes", "No", "N/A")))


# results display as visualisation ---------------------------
#| label: fig-awareness
#| fig-cap: Awareness of ETH Sustainability Department and its initiatives among ETH domain members.
#| warning: false
ggplot(data = awareness_dep_sus_ini, aes(x = Initiative, y = Count, fill = Response)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "Awareness of ETH Sustainability Department and Net Zero Initiative",
       x = "Initiative",
       y = "Count",
       fill = "Response") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# save data underlying the table ----------------------
write_csv(awareness_dep_sus_ini, "/cloud/project/data/final/awareness_department_initiatives.csv")
```

Among the initiatives, the Net Zero initiative is the most known. To explore how aware ETH members were of this intitiative further questions were asked regarding specific ETH Net Zero measures. Specifically, participants were first asked to assess their familiarity with the Net Zero on a scale from not familiar at all to very familiar and then they were asked which of these measures they heard of.

### Awareness of Net Zero measures

```{r}
## What is the awareness of the Net Zero measures among the people that have heard of the Net Zero initiative?

# data analysis --------------------------------------
awareness_net_zero_measures <- eth_dep_sus_visibility_visual %>%
  select(starts_with("heard_measure_")) %>%
  summarise_all(~sum(. == "Yes", na.rm = TRUE) / n()) %>%
  gather(key = "Measure", value = "Percentage")

# results display as visualisation --------------------------------------
#| label: fig-awareness-netzero
#| fig-cap: Awareness of Net Zero initiative among ETH domain members.
ggplot(awareness_net_zero_measures, aes(x = reorder(Measure, -Percentage), y = Percentage)) +
  geom_bar(stat = "identity", fill = "lightseagreen") +
  labs(title = "Awareness of Net Zero Measures",
       x = "Percentage",
       y = "Measure",
       fill = "Awareness") +
  coord_flip() +
  theme_minimal()

# save data underlying the table ----------------------
write_csv(awareness_net_zero_measures, "/cloud/project/data/final/awareness_net_zero_measures.csv")
```

## RQ3: What are the most effective information channels to increase the visibility of the ETH ETH Sustainability Department?

According to the previous results, the Net Zero initiative is the most known and it can therefore be implied to be the most visible. Es ist daher wichtig zu sehen, wo die Teilnehmer die Informationen erhalten, um festzustellen welches Medium für die Informationdiffusion besonders effektiv ist.

### What is the most effective information channel?

```{r}

## What information channel was the most effective?
# data analysis --------------------------------------
net_zero_learning <- eth_dep_sus_visibility_visual %>%
  filter(!is.na(learn_net_zero)) %>%
  filter(heard_net_zero == "Yes")

net_zero_info_channel_count <- net_zero_learning %>%
  count(learn_net_zero) %>%
  arrange(desc(n))

# results display as visualisation --------------------------------------
#| label: fig-netzero-measures
#| fig-cap: Awareness of the measures included in the Net Zero Initiative among ETH domain members.
ggplot(net_zero_info_channel_count, aes(x = fct_reorder(learn_net_zero, n), y = n)) +
  geom_bar(stat = "identity", fill = "lightseagreen") +
  labs(title = "Most Important Information Channel for Learning about ETH Net Zero",
       x = "Information Channel",
       y = "Frequency") +
  coord_flip()

# save data underlying the table ----------------------
write_csv(net_zero_info_channel_count, "/cloud/project/data/final/net_zero_info_channel.csv")
```

Diese Information konnte nur durch die Teilnehmer beantwortet werden konnte, die zumindest von der Net Zero initiative gehört haben. Daher wurden in einem letzten Schritt alle Teilnehmer gefragt, welcher Channel am geeignetsten wäre, um die Visibility des ETH Departments of Sustainability zu erhöhen.

### What is the most promising information channel to increase the visibility?


# Conclusions

The study While the study is not representative, it confirms the
Department's self-assessment that their visibility needs further increase.


# References


