---
title: "ETH Sustainability Department Visibility Survey"
subtitle: "Final report of the Capstone Project "
date: "05-30-2024"
author:
  - name: Ana Bendiek Laranjo
    orcid: 0009-0006-1720-6031
    email: abendiek@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
abstract: "This survey aims to assess the visibility and awareness of the ETH Sustainability department among ETH Zurich members. As the central hub for sustainability activities, ETH Sustainability is crucial in advancing sustainable development within the university and in broader society.

The department oversees various initiatives, including ETH Net Zero activities, sustainability reporting, and various projects related to sustainable travel and gastronomy. Despite its pivotal role, there is limited information on the awareness levels and engagement of the ETH community with these initiatives.

The survey seeks to understand the current recognition and understanding of ETH Sustainability’s work and services. Specifically, it will explore how well the department's efforts are known among students, faculty, and staff, and how these stakeholders perceive and engage with its activities. Additionally, the survey will gather insights on potential strategies to enhance the department's visibility and improve stakeholder engagement. The findings will contribute to the ongoing efforts to integrate sustainability more deeply into the university’s culture and operations, ensuring that ETH Zurich continues to lead in sustainable development."
license: "CC BY"
citation: 
  container-title: My Blog
  url: https://www.example.com
bibliography: references.bib
csl: apa.csl
format:
  html:
    embed-resources: true
    toc: true
    code-fold: true
pdf: default
execute:
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---

------------------------------------------------------------------------

# Introduction

Switzerland derives its concept of sustainability from the World
Commission on Environment and Development [@are2024nachhaltigkeit], also known as the Brundtland
Commission. In its 1987 report, "Our Common Future," the
Commission defined sustainable development as "Development that
satisfies the needs of the present without jeopardizing the ability of
future generations to meet their own needs" [@wced1991our].
Based on the 2030 Agenda of 2015 [@un2015transforming¨], the Federal Council adopted Switzerland's long-term climate strategy on 27 January 2021. In the "Strategie Nachhaltige Entwicklung 2030", the Confederation undertakes to consistently apply the principles of sustainable development to its own activities and units, which include the ETH Domain, in order to contribute to the achievement of the SDS 2030 goals @are2021strategie.

Within the organizational structure of ETH Zurich, the Department of
Sustainability is the central strategic-operational unit and dedicated
to enhancing ETH Zurich's contribution to sustainable development and
communicating these efforts both internally and externally. The unit was
established in 2008 and has since initiated numerous groundbreaking
projects and processes. Their responsibilty lies in the coordination of
the ETH Net Zero activities, manage sustainability reporting, oversee
the ETH Air Travel Project and the Sustainable Gastronomy Project,
compile the catalogue of sustainability-related lectures, and organize
the Public Lecture series "Sustainable Development Goals in Context" in
collaboration with ETH4D @ethsusdep2024. Despite its crucial role in the
compliance with climate change targets, there is limited information on
the awareness levels and engagement of the ETH community with these
initiatives.

The survey seeks to understand the current recognition and understanding
of ETH Sustainability’s work and services. Specifically, it will explore
how well the department's efforts are known among members of the ETH
domain, and how these stakeholders perceive and engage with its
activities. The insights of this study could contribute to improving the
department's visibility and increasing sustainability on campus.

The survey's main research question is: What is the current level of
awareness among ETH members regarding the work of and services provided
by the ETH Sustainability department, and how could it be improved?

To answer the main research question, three initial research questions
are guiding the study:

-   **RQ1:** What is the current level of awareness among ETH members
    about the ETH Sustainability Department?
-   **RQ2:** What is the current level of awareness among ETH members
    about the initiatives of the ETH Sustainability Department?
-   **RQ3:** What are the most effective information channels to
    increase the visibility of the ETH ETH Sustainability Department?

This research is exploratory and aims to set a precedent for future
information diffusion.

# Methods

The study was designed as an online survey, with data being collected
through the Google Forms platform. The study was conducted
transparently, with no incomplete disclosure of information or deception
involved. Participants were be provided with a link to the survey, which
they could access via email. They could choose to complete the survey
from any location they prefer. Furthermore, participants were free to
stop the survey at any time, ensuring their autonomy and voluntary
participation.

The study is limited to people from the ETH domain, including the
research institutions Paul Scherrer Institute (PSI), the Swiss Federal
Institute for Forest, Snow and Landscape Research (WSL), the Swiss
Federal Laboratories for Materials Science and Technology (Empa), and
the Swiss Federal Institute of Aquatic Science and Technology (Eawag).
To gain insights on the awareness levels among different affilition
groups and locations, the participants were asked to provide information
on their group and primarily working location.

The survey comprised multiple sections, each targeting specific areas of
interest:

-   Demographic Information: Participants were asked to select their
    affiliation and primary group within the ETH Zurich community.

-   Awareness and Knowledge: Questions assessed participants' awareness
    and understanding of the ETH Sustainability department, the ETH Net
    Zero initiative, the Air Travel Project, the Sustainable Gastronomy
    Project, and the Sustainable Development Goals (SDG) Public Lecture
    Series.

-   Information Sources: Participants identified where they learned
    about various sustainability initiatives (e.g., ETH website,
    lectures, seminars, advertisements on campus).

-   Engagement: Questions determined whether participants had heard of
    specific initiatives, their familiarity with the initiatives'
    scopes, and their attendance at related events.

-   Perceptions and Suggestions: Participants rated the visibility of
    the ETH Sustainability department and suggested ways to improve its
    visibility.

Responses were timestamped and collected over a one-week period,
ensuring a comprehensive snapshot of the university community's current
awareness and engagement levels. The survey was first published on May
24, 2024 and was closed on May 31, 2024 with a total of 24 participants.

The collected data were then analyzed to identify trends, gaps, and
potential strategies for enhancing the visibility and impact of the ETH
Sustainability department.

# Results

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets4)
library(dplyr)
library(ggplot2)
library(gt)
library(gtsummary)
library(knitr)
library(DT)
```

##Figures

The study shows, that overall the visibility of the ETH Department for Sustainability is low. Among the participants only
The main findings are summarised in @table.

### Awareness of ETH Sustainability Department and its initiatives

```{r}
## Which initiative is the most known?
eth_dep_sus_visibility_visual <- read_csv("/cloud/project/data/processed/eth_dep_sus_visibility_processed.csv")

# data analysis --------------------------------------

awareness_dep_sus_ini <- eth_dep_sus_visibility_visual %>%
  select(heard_eth_sus, heard_net_zero, heard_net_zero_day, heard_air_travel, heard_sus_gastronomy, heard_sdg_lecture) %>%
  summarise_all(~ mean(. == "Yes", na.rm = TRUE) * 100) %>%
  pivot_longer(cols = everything(), names_to = "Initiative", values_to = "Percentage")

# results display as visualisation ---------------------------
#| label: fig-awareness
#| fig-cap: Awareness of ETH Sustainability Department and its initiatives among ETH domain members.
#| warning: false
ggplot(data = awareness_dep_sus_ini, aes(x = Initiative, y = Percentage, fill = Initiative)) +
  geom_histogram(stat = "identity") +
  labs(title = "Awareness of ETH Sustainability Department and Net Zero Initiative",
       x = "Initiative",
       y = "Percentage") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# save data underlying the table ----------------------
write_csv(awareness_dep_sus_ini, "/cloud/project/data/final/awareness_department_initiatives.csv")
```

### Awareness of Net Zero measures

```{r}
## What is the awareness of the Net Zero measures among the people that have heard of the Net Zero initiative?

# data analysis --------------------------------------
awareness_net_zero_measures <- eth_dep_sus_visibility_visual %>%
  select(starts_with("heard_measure_")) %>%
  summarise_all(~sum(. == "Yes", na.rm = TRUE) / n()) %>%
  gather(key = "Measure", value = "Percentage")

# results display as visualisation --------------------------------------
#| label: fig-awareness-netzero
#| fig-cap: Awareness of Net Zero initiative among ETH domain members.
ggplot(awareness_net_zero_measures, aes(x = reorder(Measure, -Percentage), y = Percentage)) +
  geom_bar(stat = "identity", fill = "lightseagreen") +
  labs(title = "Awareness of Net Zero Measures",
       x = "Percentage",
       y = "Measure",
       fill = "Awareness") +
  coord_flip() +
  theme_minimal()

# save data underlying the table ----------------------
write_csv(awareness_net_zero_measures, "/cloud/project/data/final/awareness_net_zero_measures.csv")
```

### What is the most effective information channel?

```{r}

## What information channel was the most effective?
# data analysis --------------------------------------
net_zero_learning <- eth_dep_sus_visibility_visual %>%
  filter(!is.na(learn_net_zero)) %>%
  filter(heard_net_zero == "Yes")

net_zero_info_channel_count <- net_zero_learning %>%
  count(learn_net_zero) %>%
  arrange(desc(n))

# results display as visualisation --------------------------------------
#| label: fig-netzero-measures
#| fig-cap: Awareness of the measures included in the Net Zero Initiative among ETH domain members.
ggplot(net_zero_info_channel_count, aes(x = fct_reorder(learn_net_zero, n), y = n)) +
  geom_bar(stat = "identity", fill = "lightseagreen") +
  labs(title = "Most Important Information Channel for Learning about ETH Net Zero",
       x = "Information Channel",
       y = "Frequency") +
  coord_flip()

# save data underlying the table ----------------------
write_csv(net_zero_info_channel_count, "/cloud/project/data/final/net_zero_info_channel.csv")
```

### What is the most promising information channel to increase the visibility?

```{r}



```

## Tables
 


# Conclusions

The study While the study is not representative, it confirms the
Department's self-assessment regarding their visibility.

# References


